\chapter{Literature Review}
\label{chap:literature-review}

\section{Social Media Marketing and Digital Content Marketing}
\label{sec:smm-digital-content-marketing}

Social media has changed the way firms communicate with customers because it combines firm-to-customer communication with customer-to-customer circulation. Earlier work on social media describes these platforms as spaces where users create, exchange, and respond to content through networked interaction, rather than simply receiving one-way advertising messages \parencite{kaplan2010}. This makes social media marketing different from traditional promotion. Firms can still design and release messages, but the later visibility of those messages depends partly on how users, followers, employees, customers, and other connected actors share or respond to them. \textcite{mangold2009} describe social media as a hybrid element of the promotion mix because it allows firms to speak to consumers while also allowing consumers to speak directly to one another. This dual communication structure is central to the present dissertation because the WeiMai data record both firm-generated article content and the diffusion behavior that follows when marketing agents share that content through WeChat.

Digital content marketing research further emphasizes that marketing communication involves more than sending promotional information. Content can support consumer engagement, trust, and value when it provides information or experience that consumers perceive as relevant \parencite{hollebeek2019}. This point is important for social marketing systems in which firms distribute articles through agents rather than directly through a single official channel. In such systems, the same article may meet different audiences through different agents. Marketing effectiveness may therefore depend on the content itself, the social context through which it is distributed, and the fit between the two.

Empirical research on social media advertising also shows that online marketing exposure can be connected with consumer attitudes and purchase-related outcomes. For example, \textcite{duffett2015} studies Facebook advertising among Millennials and reports positive relationships between Facebook advertising exposure and purchase-related attitudes. However, the relevance of such findings to a WeChat social marketing system is not automatic. Much of this literature studies platform-level advertising or brand pages, while the present study focuses on article diffusion through identifiable marketing agents in an interior design and home decoration context. The difference matters because marketing agents do more than transmit messages. They are embedded sharers whose local audiences, job roles, and observed diffusion positions can shape how articles are exposed to readers.

Word-of-mouth and viral marketing research provides a second foundation for this dissertation. Electronic word of mouth works through staged decisions, including whether a message is opened, evaluated, and passed forward \parencite{debruyn2008}. \textcite{berger2014} also stresses that word of mouth is goal-driven: people share information for reasons such as social bonding, persuasion, emotion regulation, and self-presentation. These mechanisms suggest that diffusion cannot be fully understood as a mechanical network process. A marketing article has to be meaningful enough for readers to attend to it, and the sharing context has to create a plausible reason for the reader to read or forward it.

Taken together, social media marketing and digital content marketing research motivates the broad problem of this dissertation. Social marketing effectiveness depends on more than the existence of online platforms. It depends on how content, sharing agents, and audiences are connected in practice. This dissertation therefore treats WeChat marketing diffusion as a multi-level empirical problem rather than a simple question of whether social media marketing works.

\section{Message Content and Online Diffusion}
\label{sec:message-content-online-diffusion}

The first major stream of literature examines how message content is related to diffusion. Content matters because it gives readers a reason to pay attention, talk about a message, or rebroadcast it to others. \textcite{berger2011} show that word of mouth is shaped by product and message characteristics: interesting products can generate immediate word of mouth, while products that are cued by the surrounding environment can generate more ongoing word of mouth. This distinction is useful because online marketing diffusion extends beyond short-term attention. A message may diffuse because it is novel, emotionally engaging, practically useful, or repeatedly activated by readers' everyday environments.

Research on virality gives a more direct account of why some online content travels farther than other content. \textcite{bergermilkman2012} analyze online content virality and show that emotional and psychological content characteristics are associated with sharing. \textcite{heath2001} similarly examine emotional selection in urban legends and find that emotionally evocative content is more likely to spread. Although the empirical settings differ from WeChat marketing articles, the broader implication is relevant: readers do not forward messages randomly. Content that activates attention, emotion, usefulness, or relevance is more likely to enter interpersonal communication.

Other studies focus on observable message features in social media posts. \textcite{lahuertaotero2018} analyze Twitter activity and identify message-level features such as links, tags, emotion, and text length as factors related to retweeting and liking. \textcite{devries2012} study brand posts on Facebook fan pages and find that vividness and interactivity can be related to different forms of post popularity, such as likes and comments. These studies support the idea that marketing messages can be represented through measurable content characteristics. They also show that the same feature may not have a single universal effect across all engagement outcomes. Likes, comments, retweets, reads, reading duration, depth, and resharing can reflect different kinds of response.

This dissertation builds on this content-diffusion literature but operationalizes content in a way that matches the available WeiMai article data. Instead of relying only on manually coded emotional appeals or platform-specific features such as hashtags, the study uses an LLM-assisted content pipeline to construct topic labels, topic-score vectors, title-content semantic consistency, article length, and image-related variables. These features correspond to the Level 1 content analysis in the empirical framework. The content-level question is whether article characteristics are associated with WeChat marketing diffusion outcomes before agent-level and matching-level factors are introduced.

The literature also suggests a need for caution. Message content is not a single construct. A topic category, a title-content consistency score, a word count, and the presence of images represent different aspects of a message. A content topic may indicate what an article is about. Semantic consistency may indicate whether the title prepares readers for the body content. Word count and images may reflect richness, detail, or presentation style. Because these measures are not interchangeable, the empirical chapter should interpret each content variable according to what it measures. A positive association between title-content consistency and reach, for example, would support the view that coherent content presentation matters, but it would not prove that all kinds of content richness increase diffusion.

\section{Network Structure, Influencers, and Diffusion}
\label{sec:network-structure-influencers-diffusion}

A second stream of research examines the network side of diffusion. Social media messages do not spread in an empty space. They move through ties, audiences, and repeated exposure opportunities. \textcite{katona2011} study the diffusion of an online social network and identify network-related mechanisms such as degree and clustering effects. Their findings indicate that adoption behavior can be related to the number of adopting contacts and to the density of connections among those contacts. This supports the general claim that local network structure can shape diffusion opportunities.

Research on online content propagation reaches a similar conclusion. \textcite{yoganarasimhan2012} studies YouTube video propagation and shows that the size and structure of an author's local network are important for the diffusion of seeded content. \textcite{bakshy2012} examine information diffusion through social networks and show that network ties and social signals play a role in whether information reaches and influences others. These studies motivate the idea that who shares content matters alongside what is shared. In the WeiMai setting, marketing agents can be understood as origin points of diffusion cascades. Their observed diffusion records may reveal differences in audience reach, local sharing context, and network position.

The term ``influencer'' needs to be used carefully in this dissertation. In many social media studies, influencers are public-facing users with large audiences or high visibility. In the WeiMai data, the relevant actors are marketing agents who share company articles through WeChat. They may not be influencers in the celebrity or platform-native sense. Their importance comes from their role as embedded sharers within a firm-side social marketing system. For this reason, the dissertation uses the term ``agent'' to refer to the organizational or marketing actor who initiates an article-agent diffusion case.

Network diffusion studies also raise methodological challenges. In observational social network data, influence, homophily, and shared context are difficult to separate. \textcite{aral2009} show that influence-based contagion and homophily-driven diffusion can be confused if the empirical design does not address the difference between social influence and similarity among connected actors. \textcite{shalizi2011} make a broader methodological point: homophily and contagion are generically confounded in observational network studies unless strong assumptions or adequate controls are available. These warnings are directly relevant to this dissertation. The WeiMai data are observational, not experimental. Therefore, the empirical results should be written as associations rather than causal effects.

This caution is especially important for reconstructed network metrics. Measures such as centrality, depth, width, structural virality, and repeat exposure are useful for describing observed diffusion patterns. However, in this study they are reconstructed from the diffusion records themselves. They should not be treated as ordinary ex-ante predictors in the same way as article content features or agent attributes. This distinction shapes the Level 2 framework. Agent gender and job category can be treated as observable agent characteristics, while reconstructed centrality and related metrics should be interpreted as diffusion-pattern descriptors. They help describe heterogeneity among agents, but they do not by themselves establish that network position caused diffusion performance.

\section{Content-User Fit and Content-Agent Fit}
\label{sec:content-user-fit-content-agent-fit}

The third and most important stream of literature concerns fit. If content characteristics and network position are studied separately, the analysis may miss the possibility that the same message performs differently depending on who shares it and which audience context it enters. This is the central logic behind the title of this dissertation: one size does not fit all.

Research on referral programs provides one route into this idea. \textcite{vandenbulte2018} study a bank referral program and show how referral programs can convert social capital into economic capital. One explanation in their work is that referred customers may be better matched with the firm or product than customers acquired through other channels. Although referral programs are not identical to WeChat article diffusion, the matching logic is relevant. Social ties can help route information toward people for whom the product, service, or message is more appropriate.

\textcite{zhang2017} provide the closest foundation for the present dissertation. Their study models social media rebroadcasting by jointly considering message content, user influence, and content-user fit. This is important because it moves beyond treating content and influence as separate explanations. Their results show that rebroadcasting depends on message content, social influence, and how well a message fits the user's typical content preferences. This dissertation extends that logic from individual Twitter rebroadcasting to a firm-side WeChat marketing system. Instead of measuring fit between a message and an individual user's historical tweets, the present study measures fit between article content and marketing-agent topic context.

The shift from content-user fit to content-agent fit is more than a change in terminology. In the WeiMai setting, the agent is the point at which company content enters a local social network. An article may be technically well written or visually rich, but it may still diffuse weakly if it is shared by an agent whose audience context is not suitable for that topic. Conversely, an article that fits an agent's professional role or topic context may be more likely to reach readers who are interested in the content. This is why the final empirical framework includes Level 3 agent-topic matching rather than only article-level or agent-level models.

The matching perspective also changes the managerial implication. A content-only strategy asks which article topics or content features perform well on average. An agent-only strategy asks which agents have stronger observed diffusion capability. A matching strategy asks which content-agent combinations appear more suitable. For a social marketing system, this last question is more actionable because it can inform personalized content assignment. It suggests that firms should avoid assigning the same article uniformly to all agents when topical fit differs across agents and audiences.

At the same time, content-agent fit should not be overstated. A positive matching-diffusion association would not prove that assigning matched content causes higher diffusion unless the assignment process is experimentally or quasi-experimentally identified. In this dissertation, matching variables are used to explain observed diffusion heterogeneity in an associational framework. This is still useful because it tests whether content-agent alignment adds information beyond content-only and agent-only patterns, while keeping the causal interpretation appropriately limited.

\section{Research Gap and Conceptual Framework}
\label{sec:research-gap-conceptual-framework}

The reviewed literature provides strong reasons to study social media marketing diffusion through content, network, and fit. Prior studies show that content characteristics are related to word of mouth and online sharing \parencite{berger2011,bergermilkman2012,devries2012,lahuertaotero2018}. Network studies show that diffusion is also shaped by local structure, social ties, and the position of the actor who seeds or shares content \parencite{katona2011,yoganarasimhan2012,bakshy2012}. Matching-oriented research shows that content-user fit can matter for rebroadcasting and that social referral mechanisms may route information toward better-matched customers \parencite{vandenbulte2018,zhang2017}.

However, several gaps remain for this dissertation's setting. First, many studies examine content effects and network effects separately. This makes it difficult to know whether diffusion differences are mainly related to message characteristics, sharer characteristics, or the fit between them. Second, content-user fit has been studied in social media rebroadcasting, but there is less evidence on firm-side social marketing systems where company articles are distributed by identifiable marketing agents through WeChat. Third, prior studies often use a single unit of analysis, while the present problem requires multiple units: article-agent cases, agents, and agent-topic pairs. Mixing these units into one oversized dataset would make coefficient interpretation unclear.

The methodological literature also creates a gap between what can be measured and what can be claimed. Observational network data can describe diffusion patterns, but influence, homophily, and shared context are difficult to separate \parencite{aral2009,shalizi2011}. This dissertation therefore does not frame reconstructed network metrics as clean causal predictors. Instead, it separates variables according to their empirical role. Content features are used in the content-level analysis. Observable agent attributes and reconstructed diffusion-position descriptors are used in the agent-level analysis with careful interpretation. Matching variables are used at the agent-topic level to test whether content-agent fit is associated with diffusion performance.

The conceptual framework of the dissertation follows this three-level logic. Level 1 asks whether article content characteristics are associated with diffusion effectiveness. This level links directly to the literature on message content, virality, and brand post engagement. Level 2 asks whether agent characteristics and reconstructed diffusion-position indicators are associated with observed average diffusion patterns. This level links to research on network structure, influencers, and methodological caution in observational network analysis. Level 3 asks whether content-agent fit is associated with stronger agent-topic diffusion performance and whether this association varies across reconstructed centrality levels. This level links most directly to content-user fit and referral matching literature.

This framework supports the main argument of the thesis. Marketing diffusion effectiveness should not be treated as a one-size-fits-all problem. Content quality matters, but content alone is incomplete. Agent characteristics and observed diffusion positions matter, but agent labels alone are also incomplete. The key empirical question is whether the fit between content and agent-topic context adds explanatory value beyond the first two layers. By organizing the literature and the empirical analysis around content, agent characteristics, and content-agent matching, the dissertation provides a clearer foundation for studying personalized content assignment in a real WeChat social marketing system.
